Variational Inference for Inverse Reinforcement Learning with Gaussian Processes

### 2019-03-22 mpaper/paper.tex
Everything up to the theory section should be quite readable

\section{The Problem}

@@

Our goal is then to use VI in order to approximate $\posterior$.
Let $\approximation$ denote our approximation. VI aims to optimise this
approximation by minimising the \emph{Kullback-Leibler} (KL) divergence between
the original probability distribution and our approximation. KL divergence
(asymmetrically) measures the difference between two probability distributions
and can be defined as \cite{blei2017variational}
\begin{align*}
  \DKL{\approximation}{\posterior} &= \mathbb{E}_{\approximation}[\log\approximation - \log\posterior ] \\
                                   &= \mathbb{E}_{\approximation}[\log\approximation - \log\pfull] \\
                                   &+ \mathbb{E}_{\approximation}[\log p(\mathcal{D})].
\end{align*}
The last term is both hard to compute and constant with respect to
$\approximation$ \cite{blei2017variational}, so we can remove it from our
optimisation objective. The negation of what remains is known as the
\emph{evidence lower bound} (ELBO) and is defined as
\cite{DBLP:books/lib/Bishop07,blei2017variational}
\begin{equation} \label{eq:elbo}
  \begin{split}
    \mathcal{L} &= \mathbb{E}\left[ \log \frac{\pfull}{\approximation} \right] \\
    &= \iiint \log \frac{\pfull}{\approximation} \approximation\dx.
  \end{split}
\end{equation}
Thus, instead of minimising KL divergence, we focus on maximising $\mathcal{L}$
by optimising the values of parameters to be defined in Section \ref{sec:model}.
Note that in this paper all integrals should be interpreted as definite
integrals over the entire sample space. Also, all expected values are with
respect to $\approximation$.

@@

Here we introduce a few definitions and results from linear algebra, numerical
analysis, and measure theory that will be used later in the paper. Namely, we
will use several different vector and matrix norms, consider how an inverse of a
matrix changes with a small perturbation, and use Lebesgue's dominated
convergence theorem in order to justify the validity of our approach.

@@

\section{The Model} \label{sec:model}
% TODO: matrix notation should be at the start of The Problem

% TODO: make this fit the narrative
For any matrix $\mathbf{A}$, we will use either $A_{i,j}$ or
$[\mathbf{A}]_{i,j}$ to denote the element of $\mathbf{A}$ in row $i$ and column
$j$. Moreover, we use $\tr(\mathbf{A})$ to denote its \emph{trace} and
$\adj(\mathbf{A})$ for its \emph{adjugate} (or \emph{classical adjoint}). For
any vector $\mathbf{x}$, we write $\mathbb{R}_d[\mathbf{x}]$ to denote a vector
space of polynomials with degree at most $d$, where variables are elements of
$\mathbf{x}$, and coefficients are in $\mathbb{R}$.

In this paper, all references to measurability are with respect to the Lebesgue
measure. Similarly, whenever we consider the existence of an integral, we use
the Lebesgue definition of integration.

We keep the covariance function the same as in the work by Levine et al.
\cite{DBLP:conf/nips/LevinePK11}, which is a version of the automatic relevance
detection kernel \cite{DBLP:conf/nips/LevinePK11}:
\begin{align*}
  k(\mathbf{x}_i, \mathbf{x}_j) = \lambda_0\exp\left( \vphantom{\frac{1}{2}} \right. &-\frac{1}{2}(\mathbf{x}_i - \mathbf{x}_j)^\intercal\bm\Lambda(\mathbf{x}_i - \mathbf{x}_j) \\
                                                                                     &- \mathbbm{1}[i \ne j]\sigma^2\tr(\bm\Lambda) \left. \vphantom{\frac{1}{2}} \right).
\end{align*}
Here, $\lambda_0$ is the overall `scale' factor for how similar or distant the
states are, $\bm\Lambda = \diag(\lambda_1, \dots, \lambda_d)$ is a diagonal
matrix that determines the relevance of each feature (where $d$ denotes the
number of features), $\mathbbm{1}$ is defined as
\[
  \mathbbm{1}[b] = \begin{cases}
    1 & \mbox{if $b$ is true} \\
    0 & \mbox{otherwise},
  \end{cases}
\]
and $\sigma^2$ is set to $10^{-2}/2$ (as the original paper noted that
the value makes little difference to the performance of the algorithm
\cite{DBLP:conf/nips/LevinePK11}). We will write $\bm\lambda = (\lambda_0,
\dots, \lambda_d)^\intercal$ to refer to both $\lambda_0$ and $\bm\Lambda$ at
the same time.

Ideally, we would like to model $\bm\lambda$ with an approximating distribution.
However, due to how $p(\mathbf{u})$ has $\Kuu^{-1}$ in its expression, and the
ELBO is defined as an expectation, we are unable to show that the ELBO is
well-defined. More generally, we pose the following problem, which is open to
the best of our knowledge:
\begin{problem}
  Let $\mathbf{A}$ be a $n \times n$ matrix of coefficients, $X$ be a random
  variable, and $\mathbf{M}$ be an $n \times n$ matrix such that $M_{i,j} = f(X,
  A_{i,j})$, where $f$ is an arbitrary function. Under what circumstances does
  $\mathbb{E}[\mathbf{M}^{-1}]$ exist?
\end{problem}
While there are some obvious examples of when the required expected value
exists (e.g., $f(X, A_{i,j}) = A_{i,j}X$ for an invertible $\mathbf{A}$ and many
distributions of $X$), it would be particularly interesting to know whether the
answer is `always'. A proof of such a result would allow us to model
$\bm\lambda$ instead of treating it as a variational parameter, and would thus
guard against overfitting. For now, $\bm\lambda$ will have to be treated as a
variational parameter.

It remains to decide on the model for $\mathbf{u}$ and $\mathbf{r}$. As is
commonly done when applying VI to GPs \cite{DBLP:conf/nips/ChengB17}, we set
\begin{equation} \label{eq:approximation}
  \approximation = q(\mathbf{u}) q(\mathbf{r} \mid \mathbf{u}),
\end{equation}
where $q(\mathbf{r} \mid \mathbf{u}) = p(\mathbf{r} \mid \mathbf{u})$ and
$q(\mathbf{u}) = \mathcal{N}(\mathbf{u}; \bm\mu, \bm\Sigma)$

Ong et al. \cite{ong2018gaussian} have recently suggested that, in order to make
variational approximation of a multivariate Gaussian more scalable, the
covariance matrix should be decomposed as $\bm\Sigma =
\mathbf{B}\mathbf{B}^\intercal + \mathbf{D}^2$, where $\mathbf{B}$ is a lower
triangular $m \times p$ matrix with positive diagonal entries, and $\mathbf{D}$
is a diagonal matrix. Typically, we would set $p$ so that $p \ll m$ to get an
efficient approximation. However, as our goal is precision rather than
scalability, we will set $p = m$ and $\mathbf{D} = \mathbf{O}_m$ in order to
retain full covariance structure.

@@

The resulting model is summarised in Figure \ref{fig:graphical_model}. We rely
on $p(\mathcal{D} \mid \mathbf{r})$ as the only link between data and the model.
Since the expression for $q(\mathbf{r} \mid \mathbf{u})$ has both $\mathbf{u}$
and covariance matrices in it, $\mathbf{r}$ depends on both $\mathbf{u}$ and the
parameters of the kernel, $\bm\lambda$. The two remaining dependencies stem from
the fact that the approximating distribution for $\mathbf{u}$ is
$\mathcal{N}(\bm\lambda, \mathbf{BB}^\intercal)$.

@@

Finally, the parameters are initialised as follows:
\begin{alignat*}{3}
  \mu_i &\sim \mathcal{U}(0, 1) \quad &&\text{for } i = 1, \dots, m, \\
  \lambda_0 &\sim \chi^2_5, && \\
  \lambda_i &\sim \chi^2_1 \quad &&\text{for } i = 1, \dots, d, \\
  \diag(\mathbf{B}) &\sim \chi^2_4, && \\
  \text{the rest of } \mathbf{B} &\sim \mathcal{N}(0, 1). &&
\end{alignat*}
The initialisation of $\bm\mu$ mirrors the initialisation of $\mathbf{r}$ in
previous work by Levine et al. \cite{DBLP:conf/nips/LevinePK11}. While they have
constant initial values for $\bm\lambda$, we sample from $\chi^2$ distributions
centred around those values ($5$ for $\lambda_0$ and $1$ for any other
$\lambda_i$). The distributions for initial values of $\mathbf{B}$ are simply
set to provide a reasonable spread of positive values for the diagonal, and both
positive and negative values for all other entries in the matrix.

@@

In this section, we derive and simplify the ELBO for this (now fully specified)
model. Note that in order to keep the derivation simple, we drop all constant
terms in the expression of $\mathcal{L}$, i.e., equality is taken to mean
`equality up to an additive constant'. Also note that all expected values are
with respect to $(\mathbf{u}, \mathbf{r}) \sim q(\mathbf{u}, \mathbf{r})$.

In order to derive the ELBO, let us go back to \eqref{eq:elbo} and
write
\[
  \mathcal{L} = \mathbb{E}[\log\pfull] - \mathbb{E}[\log\approximation].
\]
By substituting in \eqref{eq:full} and \eqref{eq:approximation}, we get
\begin{align*}
  \mathcal{L} &= \mathbb{E}[\log p(\mathbf{u}) + \log p(\mathbf{r} \mid \mathbf{u}) + \log p(\mathcal{D} \mid \mathbf{r})] \\
              &- \mathbb{E}[\log q(\mathbf{u}) + \log q(\mathbf{r} \mid \mathbf{u})].
\end{align*}
Since $q(\mathbf{r} \mid \mathbf{u}) = p(\mathbf{r} \mid \mathbf{u})$, they
cancel each other out. Also notice that
\begin{align*}
  \mathbb{E}[\log p(\mathbf{u}) - \log q(\mathbf{u})] &= -\DKL{q(\mathbf{u})}{p(\mathbf{u})} \\
                                                      &= -\frac{1}{2} (\tr (\Kuu^{-1}\bm\Sigma) + \bm\mu^\intercal\Kuu^{-1}\bm\mu - m \\
                                                      &+ \log |\Kuu| - \log |\bm\Sigma|),
\end{align*}
by the definition of KL divergence between two multivariate Gaussians
\cite{kl}. Hence,
\begin{align*}
  \mathcal{L} &= \mathbb{E}\left[ \sum_{i=1}^N \sum_{t=1}^T Q_{\mathbf{r}}(s_{i,t}, a_{i,t}) - \V(s_{i,t}) \right] \\
              &- \frac{1}{2} \left(\tr \left( \Kuu^{-1}\bm\Sigma \right) + \bm\mu^\intercal\Kuu^{-1}\bm\mu + \log |\Kuu| - \log |\bm\Sigma| \right).
\end{align*}
Using the expressions for $Q_{\mathbf{r}}$ we get
\begin{align*}
  \mathcal{L} &= \mathbb{E}\left[\sum_{i=1}^N \sum_{t=1}^T r(s_{i,t}) - \V(s_{i,t}) + \gamma\sum_{s' \in \mathcal{S}} \mathcal{T}(s_{i,t}, a_{i,t}, s')\V(s') \right] \\
              &- \frac{1}{2} \left(\tr \left( \Kuu^{-1}\bm\Sigma \right) + \bm\mu^\intercal\Kuu^{-1}\bm\mu + \log |\Kuu| - \log |\bm\Sigma| \right).
\end{align*}
We can simplify $\sum_{i=1}^N\sum_{t=1}^Tr(s_{i,t})$ by defining a new vector
$\mathbf{t} = (t_1, \dots, t_{|\mathcal{S}|})^\intercal$, where $t_i$ is the
number of times the state associated with the reward $r_i$ has been visited
across all demonstrations. Then
\begin{align*}
  \mathbb{E} \left[ \sum_{i=1}^N\sum_{t=1}^Tr(s_{i,t}) \right] &= \mathbb{E}[\mathbf{t}^\intercal\mathbf{r}] = \mathbf{t}^\intercal\mathbb{E}[\mathbf{r}] \\
                                                               &= \mathbf{t}^\intercal\mathbb{E}\left[\Kru^\intercal\Kuu^{-1}\mathbf{u}\right] = \mathbf{t}^\intercal\Kru^\intercal\Kuu^{-1}\bm\mu.
\end{align*}
This allows us to simplify $\mathcal{L}$ to
\begin{align*}
  \mathcal{L} &= \mathbf{t}^\intercal\Kru^\intercal\Kuu^{-1}\bm\mu - \mathbb{E}[v] \\
              &- \frac{1}{2} \left(\tr \left( \Kuu^{-1}\bm\Sigma \right) + \bm\mu^\intercal\Kuu^{-1}\bm\mu + \log |\Kuu| - \log |\bm\Sigma| \right),
\end{align*}
where
\[
  v = \sum_{i=1}^N \sum_{t=1}^T \V(s_{i,t}) - \gamma\sum_{s' \in \mathcal{S}}
  \mathcal{T}(s_{i,t}, a_{i,t}, s')\V(s').
\]

@@

Our main goal is Theorem \ref{thm:main}, which allows us to move differentiation
inside the integral. In order to prove it, we use a number of intermediate
results. We start by stating a few derivatives of probability density functions
(PDFs) and covariance matrices, and bound their values with some
easy-to-deal-with polynomials. We then provide a sketch proof of the
measurability of MDP value functions, which is non-obvious due to their
non-trivial definition. Afterwards, we establish bounds for the value functions,
and, after another quick lemma, tackle the main proof of this paper. See Figure
\ref{fig:theorems} for an overview of how these results fit together.

@@

\section{Conclusions}
% TODO: write

% Show how we achieved our claimed contributions

Reasonable results in convergence.
More variables/information. Fewer assumptions.

We show how to avoid the deterministic training conditional assumption.

%Why doesn't it work? Perhaps a stupid bug.

>>>>

\paragraph{Notation and Conventions}

For any matrix $\mathbf{A}$, we use either $A_{i,j}$ or
$[\mathbf{A}]_{i,j}$ to denote the element of $\mathbf{A}$ in row $i$ and column
$j$. We use $\tr(\mathbf{A})$ to denote its \emph{trace} and $\adj(\mathbf{A})$
for its \emph{adjugate} (or \emph{classical adjoint}). For any vector
$\mathbf{x}$, we write $\mathbb{R}_d[\mathbf{x}]$ to denote a vector space of
polynomials with degree at most $d$, where variables are elements of
$\mathbf{x}$, and coefficients are in $\mathbb{R}$.

Throughout the paper, all integrals should be interpreted as definite integrals
over the entire sample space. When referencing measurability, we assume Lebesgue
measure in a Euclidean space with a suitable number of dimensions. Similarly,
whenever we consider the existence of an integral, we use the Lebesgue
definition of integration.

\section{The Problem} \label{sec:problem}

@@

Our goal is then to use VI in order to approximate $\posterior$.
Let $\approximation$ denote our approximation. VI aims to optimise this
approximation by minimising the \emph{Kullback-Leibler} (KL) divergence between
the original probability distribution and our approximation. KL divergence
(asymmetrically) measures the difference between two probability distributions
and can be defined as \cite{blei2017variational}
\begin{align*}
  \DKL{\approximation}{\posterior} &= \mathbb{E}_{\approximation}[\log\approximation - \log\posterior ] \\
                                   &= \mathbb{E}_{\approximation}[\log\approximation - \log\pfull] \\
                                   &+ \mathbb{E}_{\approximation}[\log p(\mathcal{D})].
\end{align*}
The last term is both hard to compute and constant with respect to
$\approximation$ \cite{blei2017variational}, so we can remove it from our
optimisation objective. The negation of what remains is known as the
\emph{evidence lower bound} (ELBO) and is defined as
\cite{DBLP:books/lib/Bishop07,blei2017variational}
\begin{equation} \label{eq:elbo}
  \begin{split}
    \mathcal{L} &= \mathbb{E}_{\approximation}\left[ \log \frac{\pfull}{\approximation} \right] \\
    &= \iiint \log \frac{\pfull}{\approximation} \approximation\dx.
  \end{split}
\end{equation}
Thus, instead of minimising KL divergence, we focus on maximising $\mathcal{L}$
by optimising the values of parameters to be defined in Section \ref{sec:model}.
Note that hereafter we drop the subscript notation, as all expected values will
be with respect to $\approximation$.

@@

We introduce a few definitions and results from linear algebra, numerical
analysis, and measure theory that will be used later in the paper. Namely, we
will use several different vector and matrix norms, consider how an inverse of a
matrix changes with a small perturbation, and introduce Lebesgue's dominated
convergence theorem which plays a major role in our theoretical results in
Section \ref{sec:proof}.

@@

\section{The Model} \label{sec:model}

In order to have a fully functional model, we still need to make several key
design decisions. In this section, we describe the covariance function used to
define the GP, consider what parameters should be used to optimise $\mathcal{L}$
and how they should be initialised, and in Section \ref{sec:elbo}, we derive our
final expression for $\mathcal{L}$.

We stick with the same covariance function as in the work by Levine et al.
\cite{DBLP:conf/nips/LevinePK11}, which is a version of the \emph{automatic
  relevance detection kernel}:
\begin{align*}
  k(\mathbf{x}_i, \mathbf{x}_j) = \lambda_0\exp\left( \vphantom{\frac{1}{2}} \right. &-\frac{1}{2}(\mathbf{x}_i - \mathbf{x}_j)^\intercal\bm\Lambda(\mathbf{x}_i - \mathbf{x}_j) \\
                                                                                     &- \mathbbm{1}[i \ne j]\sigma^2\tr(\bm\Lambda) \left. \vphantom{\frac{1}{2}} \right).
\end{align*}
Here, $\lambda_0$ is the overall `scale' factor, $\bm\Lambda = \diag(\lambda_1,
\dots, \lambda_d)$ is a diagonal matrix that determines the importance of each
feature, $\mathbbm{1}$ is defined as
\[
  \mathbbm{1}[b] = \begin{cases}
    1 & \mbox{if $b$ is true} \\
    0 & \mbox{otherwise},
  \end{cases}
\]
and $\sigma^2$ is fixed as $10^{-2}/2$, since this value has little influence on
the behaviour of the algorithm and is here as a noise factor used to avoid
singular covariance matrices \cite{DBLP:conf/nips/LevinePK11}. We will write
$\bm\lambda = (\lambda_0, \dots, \lambda_d)^\intercal$ to refer to both
$\lambda_0$ and $\bm\Lambda$ at the same time.

Ideally, we would like to model $\bm\lambda$ with an approximating distribution.
However, due to how the prior probability density function (PDF) for
$\mathbf{u}$ involves $\Kuu^{-1}$, and $\mathcal{L}$ has an expected value that
cannot be eliminated (see Section \ref{sec:elbo}), we are unable to show that
such an $\mathcal{L}$ is well-defined. More generally, we pose the following
problem, which, to the best of our knowledge, is currently open:
\begin{problem}
  Let $\mathbf{A}$ be a $n \times n$ matrix of coefficients, $X$ be a random
  variable, and $\mathbf{M}$ be an $n \times n$ matrix such that $M_{i,j} = f(X,
  A_{i,j})$, where $f$ is an arbitrary function. Under what circumstances does
  $\mathbb{E}[\mathbf{M}^{-1}]$ exist?
\end{problem}
While there are some obvious examples where the expected value exists (e.g.,
$f(X, A_{i,j}) = A_{i,j}X$ for an invertible $\mathbf{A}$ and many distributions
of $X$), it would be particularly interesting to know whether the answer is
`always'. A proof of such a result would allow us to model $\bm\lambda$ instead
of treating it as a variational parameter, and would help to guard against
overfitting. For now, $\bm\lambda$ will have to be treated as a variational
parameter.

It remains to decide on the approximation distribution for $\mathbf{u}$ and
$\mathbf{r}$. As is commonly done when applying VI to GPs
\cite{DBLP:conf/nips/ChengB17}, we set
\begin{equation} \label{eq:approximation}
  \approximation = q(\mathbf{u}) q(\mathbf{r} \mid \mathbf{u}),
\end{equation}
where $q(\mathbf{r} \mid \mathbf{u}) = p(\mathbf{r} \mid \mathbf{u})$ and
$q(\mathbf{u}) = \mathcal{N}(\mathbf{u}; \bm\mu, \bm\Sigma)$.

Ong et al. \cite{ong2018gaussian} have recently suggested that, in order to make
variational approximation of a multivariate Gaussian more scalable, the
covariance matrix should be decomposed as $\bm\Sigma =
\mathbf{B}\mathbf{B}^\intercal + \mathbf{D}^2$, where $\mathbf{B}$ is a lower
triangular $m \times p$ matrix with positive diagonal entries, and $\mathbf{D}$
is a diagonal matrix. Typically, we would set $p$ so that $p \ll m$ to get an
efficient approximation, but in this case we will simply set $p = m$ and
$\mathbf{D} = \mathbf{O}_m$ in order to retain full covariance structure.

@@

The resulting model is summarised in Figure \ref{fig:graphical_model}. We rely
on $p(\mathcal{D} \mid \mathbf{r})$ as the only link between data and our model.
Since the expression for $q(\mathbf{r} \mid \mathbf{u})$ has both $\mathbf{u}$
and covariance matrices in it, $\mathbf{r}$ depends on both $\mathbf{u}$ and the
parameters of the kernel, $\bm\lambda$. The two remaining dependencies stem from
the fact that the approximating distribution for $\mathbf{u}$ is
$\mathcal{N}(\bm\mu, \mathbf{BB}^\intercal)$.

@@

Finally, the parameters can be initialised as follows\footnote{In practice, it
  is often easier to start with a fixed $\mathbf{B} = \mathbf{I}_m$, as random
  values of $\mathbf{B}$ can often result in a near-singular $\bm\Sigma$.}:
\begin{alignat*}{3}
  \mu_i &\sim \mathcal{U}(0, 1) \quad &&\text{for } i = 1, \dots, m, \\
  \lambda_0 &\sim \chi^2_5, && \\
  \lambda_i &\sim \chi^2_1 \quad &&\text{for } i = 1, \dots, d, \\
  \diag(\mathbf{B}) &\sim \chi^2_4, && \\
  \text{the rest of } \mathbf{B} &\sim \mathcal{N}(0, 1). &&
\end{alignat*}
The initialisation of $\bm\mu$ mirrors the initialisation of $\mathbf{r}$ in
previous work by Levine et al. \cite{DBLP:conf/nips/LevinePK11}. In contrast,
while they have constant initial values for $\bm\lambda$, we sample from
$\chi^2$ distributions centred around those values ($5$ for $\lambda_0$ and $1$
for any other $\lambda_i$). The distributions for initial values of $\mathbf{B}$
are simply set to provide a reasonable spread of positive values for the
diagonal, and both positive and negative values for all other entries in the
matrix.

@@

It remains to express $\mathcal{L}$ for our (now fully specified) model. Note
that in order to keep the derivation simple, we drop all constant terms in the
expression of $\mathcal{L}$, i.e., equality is taken to mean `equality up to an
additive constant'.

Firstly, let us return to \eqref{eq:elbo} and write
\[
  \mathcal{L} = \mathbb{E}[\log\pfull] - \mathbb{E}[\log\approximation].
\]
By substituting in \eqref{eq:full} and \eqref{eq:approximation}, we get
\begin{align*}
  \mathcal{L} &= \mathbb{E}[\log p(\mathbf{u}) + \log p(\mathbf{r} \mid \mathbf{u}) + \log p(\mathcal{D} \mid \mathbf{r})] \\
              &- \mathbb{E}[\log q(\mathbf{u}) + \log q(\mathbf{r} \mid \mathbf{u})].
\end{align*}
Since $q(\mathbf{r} \mid \mathbf{u}) = p(\mathbf{r} \mid \mathbf{u})$, they
cancel each other out. Also notice that
\begin{align*}
  \mathbb{E}[\log p(\mathbf{u}) - \log q(\mathbf{u})] &= -\DKL{q(\mathbf{u})}{p(\mathbf{u})} \\
                                                      &= -\frac{1}{2} (\tr (\Kuu^{-1}\bm\Sigma) + \bm\mu^\intercal\Kuu^{-1}\bm\mu - m \\
                                                      &+ \log |\Kuu| - \log |\bm\Sigma|),
\end{align*}
by the definition of KL divergence between two multivariate Gaussians
\cite{kl}. Hence,
\begin{align*}
  \mathcal{L} &= \mathbb{E}\left[ \sum_{i=1}^N \sum_{t=1}^T Q_{\mathbf{r}}(s_{i,t}, a_{i,t}) - \V(s_{i,t}) \right] \\
              &- \frac{1}{2} \left(\tr \left( \Kuu^{-1}\bm\Sigma \right) + \bm\mu^\intercal\Kuu^{-1}\bm\mu + \log |\Kuu| - \log |\bm\Sigma| \right).
\end{align*}
Using the expressions for $Q_{\mathbf{r}}$ we get
\begin{align*}
  \mathcal{L} &= \mathbb{E}\left[\sum_{i=1}^N \sum_{t=1}^T r(s_{i,t}) - \V(s_{i,t}) + \gamma\sum_{s' \in \mathcal{S}} \mathcal{T}(s_{i,t}, a_{i,t}, s')\V(s') \right] \\
              &- \frac{1}{2} \left(\tr \left( \Kuu^{-1}\bm\Sigma \right) + \bm\mu^\intercal\Kuu^{-1}\bm\mu + \log |\Kuu| - \log |\bm\Sigma| \right).
\end{align*}
We can simplify $\sum_{i=1}^N\sum_{t=1}^Tr(s_{i,t})$ by defining a new vector
$\mathbf{t} = (t_1, \dots, t_{|\mathcal{S}|})^\intercal$, where $t_i$ is the
number of times the state associated with reward $r_i$ has been visited
across all demonstrations. Then,
\begin{align*}
  \mathbb{E} \left[ \sum_{i=1}^N\sum_{t=1}^Tr(s_{i,t}) \right] &= \mathbb{E}[\mathbf{t}^\intercal\mathbf{r}] = \mathbf{t}^\intercal\mathbb{E}[\mathbf{r}] \\
                                                               &= \mathbf{t}^\intercal\mathbb{E}\left[\Kru^\intercal\Kuu^{-1}\mathbf{u}\right] = \mathbf{t}^\intercal\Kru^\intercal\Kuu^{-1}\bm\mu.
\end{align*}
This allows us to simplify $\mathcal{L}$ to
\begin{align*}
  \mathcal{L} &= \mathbf{t}^\intercal\Kru^\intercal\Kuu^{-1}\bm\mu - \mathbb{E}[v] \\
              &- \frac{1}{2} \left(\tr \left( \Kuu^{-1}\bm\Sigma \right) + \bm\mu^\intercal\Kuu^{-1}\bm\mu + \log |\Kuu| - \log |\bm\Sigma| \right),
\end{align*}
where
\[
  v = \sum_{i=1}^N \sum_{t=1}^T \V(s_{i,t}) - \gamma\sum_{s' \in \mathcal{S}}
  \mathcal{T}(s_{i,t}, a_{i,t}, s')\V(s').
\]

@@

Our main goal is Theorem \ref{thm:main}, which allows us to move differentiation
inside the integral. In order to prove it, we use a number of intermediate
results. We start by stating a few derivatives of PDFs and covariance matrices,
and bound their values with some easy-to-deal-with polynomials. We then provide
a sketch proof of the measurability of MDP value functions, which is non-obvious
due to their non-trivial definition. Afterwards, we establish bounds for the
value functions, and, after another quick lemma, tackle the main proof of this
paper. See Figure \ref{fig:theorems} for an overview of how these results fit
together.

@@

\section{Conclusion}
% TODO: write
% Show how we achieved our claimed contributions

\begin{itemize}
\item Why my theoretical contributions are important...
\item Reasonable results with convergence: policies do converge to optimal
  values, even at the extremes (i.e., $0$ and $1$).
\item Shown how to eliminate the deterministic training conditional
  assumption---a common weakness of previous approaches.
\item Being able to model rewards using full probability distributions without
  limiting assumptions opens up many new research directions.
\item My excuse for the buggy implementation...
\end{itemize}
